Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-10 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Add a fourth reason for natural deduction style.

The natural deduction style was chosen for three reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiarized with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}.

>>>>

The natural deduction style was chosen for four reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiarized with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}. And finally, in comparison to other kinds of proof systems (e.g. resolution, tableaux, sequent calculi), natural deduction can be considered less technical, more human-readable and more intuitive, because it relies on natural principles of reasoning such as modus ponens (implication elimination) and reasoning by assumption (implication introduction); these qualities are conducive to rendering the formalizations of ontological arguments accessible to a wider audience.
